Supplementary Information: Vulnerability of tree growth

### 2025-03-26 doc/manuscript_hkk_drought_sensitivity.Rmd
discussion skeleton

<!--KAT suggestion for new intro paragraph (would replace next paragraph)-->
- *In forests worldwide, intense drought is becoming more frequent, affecting forest demography, diversity, and  C cycling.*
- *Understanding these impacts is an important research priority, particularly for tropical forests, which harbor high species diversity and are critical in the global C cycle.* 
- *However, study of tropical tree woody growth responses to drought is inhibited by the fact that few tropical species form rings and long-term annual records are rare [@zuidema_tropical_2022].*
- *We know that drought characteristics, species traits, and microenvironment all affect tree growth responses.* 
- *However, we know little about their combined effects or potential interactions, which could fundamentally alter our understanding of forest responses to drought.*
<!--The above statement is true at least to my knowledge offhand, but we need to check--> 
- *Specifically, if drought tolerance is influenced independently by drought characteristics, species traits, and microenvironment, it is relatively straightforward to predict tree drought responses; for example, we'd expect a species that has proved relatively resistant to past droughts to be among the most drought-resistant species in any microhabitat and through any drought. *
- *In contrast, if these factors interact, the species and individuals that exhibit resistance to one drought may prove much more vulnerable in the next. The resultant amplification of the complexity and diversity of drought responses may act as a mechanism for promoting species diversity and stabilizing ecosystem function as drought regimes intensify.*

<!--PARAGRAPH ON IMPORTANCE OF DROUGHT, HOW OUR UNDERSTANDING REMAINS LIMITED, PARTICULARLY FOR SEASONAL TROPICAL FORESTS-->

Increasing drought risk is threatening demographic processes in global forests and consequently their consistent contributions to the land carbon sink [IPCC].  
- Every year, woody growth of trees in tropical forests removes roughly `r round (150*1/6,0)` Gt CO~2~ from the atmosphere [@beer_terrestrial_2010;@anderson-teixeira_carbon_2021;@anderson-teixeira_carbon_2016], contributing to a net biomass increase of ~7 Gt CO~2-eq~ [@harris_global_2021] that offsets ~`r round(7/36.3*100,-1)`% of anthropogenic fossil fuel emissions [@friedlingstein_global_2022].<!--copied from our grant proposal - something like this is more specific and perhaps more compelling-->
- Moreover, woody growth has one of the longest residence times in terrestrial carbon pool, contributing to long-lasting impacts on carbon removal from the atmosphere [@yang_variations_2021; @muller-landau_patterns_2021].  
- However, tree growth is vulnerable to drought, the frequency and intensity of which are increasing across the much of tropics [@tao_increasing_2022]. <!--and there is some evidence that stand-level vulnerability is increasing [@luo_tropical_2022; @tao_increasing_2022].-->
- (We don't know very much about woody growth responses, as few tropical species form rings and long-term annual records are rare [@zuidema_tropical_2022].)
- Drought sensitivity is often understood as a species trait, but it can vary substantially among drought events [] and among individuals based on their characteristics [@bennett_larger_2015; @mcgregor_tree_2021], compounding uncertainties in predicting forest responses.  
- With changing climate patterns across the global tropics, emergence of novel climatic regimes like "very extreme droughts" in recent decades [@dahinden_future_2017; @luo_tropical_2022], there is an urgent need to understand the drivers of this variation, to be able to predict and respond to forest drought responses.

<!--PARAGRAPH ON DROUGHT CHARACTERISTICS-->
Drought characteristics can influence climatic drivers of tree growth and their timing, and affect drought sensitivity of tropical trees.
- Tree growth in both everwet and seasonally dry tropical forests show predictable seasonal patterns [@garcía-cervigón_climate_20200; @giraldo_tree_2023], but with differences among these patterns.
- Droughts are characterised by anomalously hot and/or dry conditions, but these can occur at any time during the seasonal phenology of tree growth.
- The effect of drought timing can be more pronounced in seasonally dry tropical forests because of strong seasonality in climate and consequently on photosynthesis, allocation and growth (including dry seasons unfavourable to growth).   
- They are also at thermal/water stress tolerance thresholds, making them more vulnerable to drought [@allen_will_2017], potentially explaining stand-level patterns
of drought-associated water stress  [@bauman_tropical_2022; @bennett_sensitivity_2023; @aguirre-gutiérrez_drier_2019].
- Analyses to date have found that the woody growth of tropical trees <!--decreases with temperature[@zuidema_tropical_2022;@clark_annual_2010;@clark_annual_2021; @vlam_temperature_2014] and -->is particularly vulnerable to dry season precipitation[@zuidema_tropical_2022;@clark_annual_2010;@clark_annual_2021]; however, these analyses represent only a very limited set of tropical tree species and climates. 
- Trees in seasonally dry tropical forests exhibit a mix of strategies - along a spectrum of conservative to acquisitive water-use - that support survival and growth despite strong seasonal hot/dry stress, which might confer differential advantages in drought conditions.
<!-- - Trees in seasonally dry forests are routinely exposed to hot, dry conditions in the dry season and may have evolutionary strategies like dry-season deciduousness and <!-- - Morevoer, besides broad patterns at the stand level, species- and individual-level heterogeneity can lead to divergent responses with consequences for stand composition.   
- Some of the discrepancies between expectations from trees and observations at the stand-level may be resolved by considering factors that determine drought sensitivity across species and individuals  -->

@@

<!--PARAGRAPH ON HOW MICROENVIRONMENT SHAPES DROUGHT RESPONSES-->
Individual growth responses to drought can also depend on the specific microenvironments they experience that can lead to distict atmospheric and hydrological stresses with ecological consequences.  
- Larger trees suffer more growth declines during drought [@bennett_larger_2015], exposed crowns -> more thermal stress [@vinod_thermal_2023] although crown exposure -> more light -> more growth in normal years. 
- ecological timescales - e.g. distribution of trees in relation to wetness  
-  Species distribution of evergreen species covarying with soil moisture [@kunert_leaf_2021] and potentially affecting survival and growth.  
- Some of these adaptations may confer drought sensitivity and buffer stem growth declines during drought years, or conversely, may tradeoff with advantages in normal years, leading to a diversity of responses within a drought event.  
- Moreover, drought characteristics can positively or negatively interfere with these factors, leading to consistent or heterogenous sensitivities across drought events.

@@

 <!-- Within species, size, exposure and location can affect sensitivity to drought.  
- Large trees tend to undergo greater growth declines during drought compared to smaller trees [e.g., @bennett_larger_2015; @mcgregor_tree_2021; @anderson-teixeira_joint_2022].   
- It remains poorly understood the extent to which this is shaped by tree size itself, crown exposure, water access, and traits that tend to covary with size (e.g., decidiousness) -- all of which interact to shape drought resistance (Fig. `r fig_DAG`).  
- There is theory and evidence that tree size itself matters.  
- Theoretically, we expect that greater height makes trees more vulnerable to drought based on the physics of hydraulic flow through a porous medium, as described by Darcy's law [@mcdowell_darcy_2015; @fernández-de-uña_role_inpress].
- Height... [see refs in @vinod_thermal_2023; @olson_plant_2018; @couvreurWaterTransportTall2018].
- As tree size increases, leaves exert lower control over hydraulic resistance [@wolfe_leaves_2023].
- @chen_hydraulic_2022  
- There is theory and evidence that crown exposure matters [ @vinod_thermal_2023;  @refs_in_ vinod_thermal_2023; @scharnweber_confessions_2019].
- Microclimate buffering leads to cooler, moister understory air [@vinod_thermal_2023].
- Soils under closed canopies would also be cooler during hot times of the year [@lembrechts_global_2022].
- Reduced evaporative demand would also make them moister, and this might be added to by hydraulic redistribution.
- Trees with exposed crowns suffered significant crown dieback at greater rates in the 2012-16 CA drought [@ma_tree_2023].  
- Water access....  
- Larger trees have larger root systems, but do not necessarily access deeper water [@ref_from_Panama]  
- Even when trees are accessing deeper water, this does not mean that they're in better shape during drought. Rather, trees that rely on regular access to deep water may be more vulnerable during severe droughts when those sources are depleted [@chitra-tarak_hydraulicallyvulnerable_2021].  
- indeed, there is evidence that trees near streams undergo greater growth declines [@mcgregor_tree_2021] and increases in mortality [@zuleta] during drought
- rather than necessarily helping during drought, water access will shape the size and traits of species living in habitat, with stream habitats tending to have larger trees [@ref] and more evergreen trees, and also their average growth rate--->

@@

<!-- - **habitat** : water availability is a key driver of tropical tree growth [@wagner_water_2012]. 
- **leaf habit** : drought resistance is higher in deciduous species because of leaf strategies that minimise water loss during months of high vulnerability. Deciduous and evergreen species have differential sensitivity to drought [@desouza_drought_2020].    
- **tree size** : larger trees face higher risk of mortality during drought, as well as greater growth reductions [e.g., @bennett_larger_2015; @mcgregor_tree_2021; @anderson-teixeira_joint_2022].  
- **exposure** : trees with higher exposure because of their canopy position have lower drought resistance than trees with lower exposure due to the direct effects of temperature and vapour pressure deficit.    
- **leaf habit x exposure** : species canopy strategies along with their leaf habit could exacerbate or counteract drought vulnerability [@rahman_speciesspecific_2019]. Under high exposure, deciduous species are potentially more drought resistant than evergreen species, while the pattern could be less clear under low exposure.  
- **leaf habit x habitat** : tropical evergreen and deciduous species have different habitat preferences [@kunert_leaf_2021] that could affect their drought resistance.   -->

@@

Our results show that tree drought sensitivity can be jointly shaped by drought characteristics, species adaptations and local environmental conditions.
We found that some of the variation in sensitivity of tree growth to drought can be explained by a combination of species-level deciduousness, and individual level crown exposure, water availability and other size effects.  
Taken together, our analysis of tree growth in two different drought years, and spanning meaningful variation, shows that species and individuals can respond differently to different drought events.  
Despite stand-level growth declines in drought years, the heterogeneity in individual and species responses suggest insurance effects in the community with consequences for ecosystem stability.

Unordered points from Introduction
- Many hydraulic-related traits vary with tree height [ @vinod_thermal_2023], including the frequency of dry season deciduous leaf loss -- both within species and at the community level [@condit_ref; @meakem].  *caveat for species-level traits*

*for where else might they be allocating to?*
- Some evidence that both understory and emergent species can have reduced survival during drought [@machado_forest_2023].  
- ENSO droguht changed regeneration dynamics in Thailand [@nutiprapun_effects_2023]
- deciduous species have higher survival under multi-year droughts [@aguirre-guiterrez refs]

@@

- Our finding that a wet season drought had bigger impact calls into question the generality of the findings of @zuidema_tropical_2022, which found that in species with tree-ring chronologies, dry season drought was most impactful. However, care must be taken in interpretation, as the 2015-16 ENSO was stronger.
- Afzelia xylocarpa, one of the tree ring species had the most distinct (positive) sensitivity in the dry season drought *on how representative sampling is important*

>>>>

<!--KAT suggestion for new intro paragraph (would replace next paragraph)-->
In forests worldwide, intense drought is becoming more frequent, affecting forest demography, diversity, and  C cycling. [IPCC]
- Understanding these impacts is an important research priority, particularly for tropical forests, which harbor high species diversity and are critical in the global C cycle.
- However, study of tropical tree woody growth responses to drought is inhibited by the fact that few tropical species form rings and long-term annual records are rare [@zuidema_tropical_2022].
- We know that drought characteristics, species traits, and microenvironment all affect tree growth responses.  
- However, we know little about their combined effects or potential interactions, which could fundamentally alter our understanding of forest responses to drought.  
<!--The above statement is true at least to my knowledge offhand, but we need to check--> 
- Specifically, if drought tolerance is influenced independently by drought characteristics, species traits, and microenvironment, it is relatively straightforward to predict tree drought responses; for example, we'd expect a species that has proved relatively resistant to past droughts to be among the most drought-resistant species in any microhabitat and through any drought. 
- In contrast, if these factors interact, the species and individuals that exhibit resistance to one drought may prove much more vulnerable in the next. The resultant amplification of the complexity and diversity of drought responses may act as a mechanism for promoting species diversity and stabilizing ecosystem function as drought regimes intensify.

<!--PARAGRAPH ON IMPORTANCE OF DROUGHT, HOW OUR UNDERSTANDING REMAINS LIMITED, PARTICULARLY FOR SEASONAL TROPICAL FORESTS-->
<!-- Increasing drought risk is threatening demographic processes in global forests and consequently their consistent contributions to the land carbon sink [IPCC].   -->
<!-- - Every year, woody growth of trees in tropical forests removes roughly `r round (150*1/6,0)` Gt CO~2~ from the atmosphere [@beer_terrestrial_2010;@anderson-teixeira_carbon_2021;@anderson-teixeira_carbon_2016], contributing to a net biomass increase of ~7 Gt CO~2-eq~ [@harris_global_2021] that offsets ~`r round(7/36.3*100,-1)`% of anthropogenic fossil fuel emissions [@friedlingstein_global_2022].copied from our grant proposal - something like this is more specific and perhaps more compelling -->
<!-- - Moreover, woody growth has one of the longest residence times in terrestrial carbon pool, contributing to long-lasting impacts on carbon removal from the atmosphere [@yang_variations_2021; @muller-landau_patterns_2021].  
- However, tree growth is vulnerable to drought, the frequency and intensity of which are increasing across the much of tropics [@tao_increasing_2022]. <!--and there is some evidence that stand-level vulnerability is increasing [@luo_tropical_2022; @tao_increasing_2022].-->
<!-- - (We don't know very much about woody growth responses, as few tropical species form rings and long-term annual records are rare [@zuidema_tropical_2022].)
- Drought sensitivity is often understood as a species trait, but it can vary substantially among drought events [] and among individuals based on their characteristics [@bennett_larger_2015; @mcgregor_tree_2021], compounding uncertainties in predicting forest responses.  
- With changing climate patterns across the global tropics, emergence of novel climatic regimes like "very extreme droughts" in recent decades [@dahinden_future_2017; @luo_tropical_2022], there is an urgent need to understand the drivers of this variation, to be able to predict and respond to forest drought responses.   
 -->

<!--PARAGRAPH ON DROUGHT CHARACTERISTICS-->
Drought characteristics can influence climatic drivers of tree growth and their timing, and affect drought sensitivity of tropical trees.
- Tree growth in both everwet and seasonally dry tropical forests show predictable seasonal patterns [@garcía-cervigón_climate_20200; @giraldo_tree_2023], but with differences among these patterns. 
- Drought definitions are many, but here we refer to hot dry conditions anomalous from long-term means
- Drought is anomalously hot/dry conditios, but different types based on which variable is anomalous.  
- Droughts are characterised by anomalously hot and/or dry conditions, but these can occur at any time during the seasonal phenology of tree growth.  
- The effect of drought timing can be more pronounced in seasonally dry tropical forests because of strong seasonality in climate and consequently on photosynthesis, allocation and growth (including dry seasons unfavourable to growth).   
- They are also at thermal/water stress tolerance thresholds, making them more vulnerable to drought [@allen_will_2017], potentially explaining stand-level patterns
of drought-associated water stress  [@bauman_tropical_2022; @bennett_sensitivity_2023; @aguirre-gutiérrez_drier_2019].
- Analyses to date have found that the woody growth of tropical trees <!--decreases with temperature[@zuidema_tropical_2022;@clark_annual_2010;@clark_annual_2021; @vlam_temperature_2014] and -->is particularly vulnerable to dry season precipitation[@zuidema_tropical_2022;@clark_annual_2010;@clark_annual_2021]; however, these analyses represent only a very limited set of tropical tree species and climates.   
- DRY SEASON IS NOT DROUGHT; dry season has hot, dry conditions periodic and predictable, but anomalously hot, dry conditions, unpredictable.  
- Trees in seasonally dry tropical forests exhibit a mix of strategies - along a spectrum of conservative to acquisitive water-use - that support survival and growth despite strong seasonal hot/dry stress, which might confer differential advantages in drought conditions.

@@

<!--PARAGRAPH ON HOW MICROENVIRONMENT SHAPES DROUGHT RESPONSES-->
Individual growth responses to drought can also depend on the specific microenvironments they experience that can lead to distict atmospheric and hydrological stresses with ecological consequences.  
- Larger trees suffer more growth declines during drought [@bennett_larger_2015], exposed crowns -> more thermal stress [@vinod_thermal_2023] although crown exposure -> more light -> more growth in normal years. 
- ecological timescales - e.g. distribution of trees in relation to wetness  
-  Species distribution of evergreen species covarying with soil moisture [@kunert_leaf_2021] and potentially affecting survival and growth.  
- Larger trees have larger root systems, but do not necessarily access deeper water [@ref_from_Panama]  
- Even when trees are accessing deeper water, this does not mean that they're in better shape during drought. Rather, trees that rely on regular access to deep water may be more vulnerable during severe droughts when those sources are depleted [@chitra-tarak_hydraulicallyvulnerable_2021].  
- indeed, there is evidence that trees near streams undergo greater growth declines [@mcgregor_tree_2021] and increases in mortality [@zuleta] during drought  
- Some of these adaptations may confer drought sensitivity and buffer stem growth declines during drought years, or conversely, may tradeoff with advantages in normal years, leading to a diversity of responses within a drought event.  
- Moreover, drought characteristics can positively or negatively interfere with these factors, leading to consistent or heterogenous sensitivities across drought events.

@@

 <!-- Within species, size, exposure and location can affect sensitivity to drought.  
- There is theory and evidence that tree size itself matters.  
- Theoretically, we expect that greater height makes trees more vulnerable to drought based on the physics of hydraulic flow through a porous medium, as described by Darcy's law [@mcdowell_darcy_2015; @fernández-de-uña_role_inpress].
- Height... [see refs in @vinod_thermal_2023; @olson_plant_2018; @couvreurWaterTransportTall2018].
- As tree size increases, leaves exert lower control over hydraulic resistance [@wolfe_leaves_2023].
- @chen_hydraulic_2022  
- There is theory and evidence that crown exposure matters [ @vinod_thermal_2023;  @refs_in_ vinod_thermal_2023; @scharnweber_confessions_2019].
- Microclimate buffering leads to cooler, moister understory air [@vinod_thermal_2023].
- Soils under closed canopies would also be cooler during hot times of the year [@lembrechts_global_2022].
- Reduced evaporative demand would also make them moister, and this might be added to by hydraulic redistribution.
- Trees with exposed crowns suffered significant crown dieback at greater rates in the 2012-16 CA drought [@ma_tree_2023].  
- rather than necessarily helping during drought, water access will shape the size and traits of species living in habitat, with stream habitats tending to have larger trees [@ref] and more evergreen trees, and also their average growth rate--->

@@

<!-- - **habitat** : water availability is a key driver of tropical tree growth [@wagner_water_2012]. 
- **leaf habit** : drought resistance is higher in deciduous species because of leaf strategies that minimise water loss during months of high vulnerability. Deciduous and evergreen species have differential sensitivity to drought [@desouza_drought_2020].    
- **leaf habit x exposure** : species canopy strategies along with their leaf habit could exacerbate or counteract drought vulnerability [@rahman_speciesspecific_2019]. Under high exposure, deciduous species are potentially more drought resistant than evergreen species, while the pattern could be less clear under low exposure.  
- **leaf habit x habitat** : tropical evergreen and deciduous species have different habitat preferences [@kunert_leaf_2021] that could affect their drought resistance.   -->

@@

<!---CONCLUSIONS---->
We show strong evidence that tropical tree drought sensitivity can be jointly and interactively shaped by drought characteristics, species adaptations and local environmental conditions (Table 1).
Analysing two droughts in a 14-year dendrometer band timeseries, we found that tropical tree species and individuals grew less than average in drought years, reflecting in lower plot-level growth (Fig 2).  
Comparing across droughts, we found that despite the shorter duration of drought conditions, the wet-season drought elicited stronger responses across trees, but especially so for deciduous species that are expected to have stronger seasonality in growth phenology.  
Interestingly, in the wet-season drought, we also show that evergreen and deciduous species had divergent responses along a wetness gradient; evergreen trees fared better and deciduous species suffered worse declines in wetter sites.  
Further, besides consistent negative effects of crown exposure, we found that the drivers of variation among species and individuals in drought sensitivity were dissimilar between the drought events. 
Water availability buffered exposure-associated growth declines through different mechanisms in the two different droughts - larger trees (with likely deeper roots) in the dry-season drought and trees in wetter sites in the wet-season drought suffered smaller declines in growth.  
Taken together, our analysis of tree growth in two different drought years, and spanning meaningful variation, shows that species and individuals can respond differently to different drought events.  
Despite stand-level growth declines in drought years, we show that these broad patterns mask enormous heterogeneity in individual and species responses to drought in tropical forests with possible consequences for the maintenance of species diveristy and ecosystem stability.

<!----Limitations in filling gap---->
a: Although our analysis spans representative spatial and ecological variation, we are limited in quantitatively analysing differences among droughts and variation in drought characteristics, because of low sample size.  
-   Our analysis spans ecological and spatial/environmental variation realistic to tropical trees, and beyond previous such analyses.
- But given the relative shorter duration of the timeseries, the effort required to collect these data, and the unpredictability of drought events, our analysis only included two specific droughts.
- Thus, quantitative analyses parsing out the specific effects of drought characteristics like relative influence of timing and degree of anomaly is currently impossible, limiting interpretations.  
- However, as the record continues to grow, so does the potential to answer these questions.

b: We analysed species traits as static, but we might be missing intraspecific and plastic variation in drought sensitivity traits, as well as other axes of trait variation that might explain variation in drought sensitivity.
- Many hydraulic-related traits vary with tree height [ @vinod_thermal_2023], including the frequency of dry season deciduous leaf loss -- both within species and at the community level [@condit_ref; @meakem].  *caveat for species-level traits*  
- While leaf deciduousness was the main axis of hydraulic conservative strategy that we considered, leaf-level stomatal regulation and belowground root loss etc. are other potential strategies for conservative water use, and our interpretation of species patterns may be limited by our understanding of these processes across species.  
- Surprisingly, although deciduousness may have had an advantage in the dry season drought, because this strategy -> conservative water use in the dry season, species differences in this drought were not predicted by deciduousness.

<!----Limitations in generalisation---->
a: Differential allocation to growth may not mean negative outcomes, it might mean demographic trade-offs
- Differences in allocation to growth may not be the complete picture - may have altered allocation to mortality or reproduction.  
- Some evidence that both understory and emergent species can have reduced survival during drought [@machado_forest_2023].  *for where else might they be allocating to?*
- 2015 ENSO drought changed regeneration dynamics in Thailand [@nutiprapun_effects_2023]
- also NSCs and then compensatory growth
- deciduous species have higher survival under multi-year droughts [@aguirre-guiterrez refs]

b: Tropical dry forests also represent periodic hot/dry conditions, leading to adaptations or other genetic variation for resistance, but this might not hold in other bioclimatic zones where ecological variability is different.  
- Trait variation across forest and bioclimatic types
- Careful interpretation across forest types with different adaptive pressures.  
- However, some generalisation is possible because despite low seasonality in climatic conditions, everwet forest species also show seasonal growth patterns.

<!----Contributions beyond---->
Despite consistent growth declines at the plot level across drought events, we show that this scale obscures a variety of ecological responses at the species and tree level that are heterogeneous across drought events.  
- Our finding that a wet season drought had bigger impact calls into question the generality of the findings of @zuidema_tropical_2022, which found that in species with tree-ring chronologies, dry season drought was most impactful. However, care must be taken in interpretation, as the 2015-16 ENSO was stronger. 
- Influence of deciduousness was different in the two different droughts. 
- *Afzelia xylocarpa*, one of the tree ring species had the most distinct (positive) sensitivity in the dry season drought, but a large negative sensitivity in the wet season drought - one of the most distinct responses.  
- More generally, tree ring and census estimates of drought sensitivity in seasonally dry tropical forests may be biased towards fast growing (measurable using tape) or dry-associated species (that form annual tree rings) - which might have been capturing only the more dramatic effects.
- Distinct responses of species and individuals to drought characteristics suggests potential spatiotemporal insurance effects among tropical tree response to drought.

<!----Science is better now---->
Drought sensitivity is often defined as a static species trait but we show dimensions beyond that with possible consequences for management and restoration 
- Although net decrease at the plot level (agreement with landscape-scale in @aguirre-guiterrez), we show evidence that the same strategies are not uniformly successfully across spatiotemporal climatic variation.  
- Frameworks that include ecological complexity and covarying traits with environment like @trugman_why_2021 also assume individual trees to have consistent sensitivity across events, but our results demonstrate temporal dimensions of variation, at least partially attributable to drought characteristics.  
- Our results indicate that drought responses in tropical trees may not be a fixed response across events, but jointly shaped by...
- Given these inconsistencies, diverse stands that may represent greater variation in ecological and evolutionary strategies, may have mechanisms for stable functioning under future droughts.

<!---SPECIES EFFECTS--->

@@
